Binning Strategies and Related Loss for Large Data

### 2015-04-15 Paper.Rnw
last (?) new paragraph: choosing the binwidth
add references to binning loss work by Scott in section 4

Note that even though these losses may turn out to be substantial, it is, in fact, a huge gain with respect to the original scatterplot, where information is masked in large data situations due to over-plotting of points.

>>>>

Note that even though these losses may turn out to be substantial, it is, in fact, a huge gain with respect to the original scatterplot, where information is masked in large data situations due to over-plotting of points. \ktm{The idea of loss from one-dimensional binning was explored by Scott using mean squared error as a loss function where the number of bins could be optimized for the construction of histograms \citep{scott1979}. He later extended this discussion to two-dimensional binning, where he compared the mean squared error loss for hexagonal, rectangular and triangular binning; finding that hexagonal and rectangular binning performed similarly, both far superior to triangular binning \citep{scott1992}. We will take a similar approach to quantifying loss resulting from the binning algorithms detailed in Section\ref{GenBinning} above. }
